---
title: "Examples 2"
output:
  html_document:
    toc: true
    toc_float:
      smooth_scroll: false
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(aggrid)
library(dplyr)
library(htmlwidgets)
```

## Selection

### Row Selection

#### CheckboxSelection

```{r}
head(iris, n = 10) |>
  aggrid(checkboxSelection = T)
```

#### Single Selection
```{r}
head(iris, n = 10) |>
  aggrid(checkboxSelection = T,rowSelection = "single",suppressRowClickSelection = T)
```

#### selectedRows
```{r}
head(iris, n = 10) |>
  aggrid(checkboxSelection = T,selectedRows = 1:3)
```

#### selectedRows all

I set a convenience parameter for selecting all rows.
```{r}
head(iris, n = 10) |>
  aggrid(checkboxSelection = T,selectedRows = "all")
```

## Sparkline

### line plot and column plot

```{r}
mtcars |>
  dplyr::group_by(cyl) |>
  dplyr::summarize(mpg_line = list(mpg)) |>
  aggrid() |>
  ag_col_render(mpg_line, cellRenderer = "agSparklineCellRenderer")
```

Note in the snippet above that specifying an `agSparklineCellRenderer` will display the data using the default `line` sparkline. 


Sparklines are customised by supplying `sparklineOptions` to the `cellRendererParams` on the Sparkline Cell Renderer as shown below. For example：

### bar plot

```{r}
head(mtcars, n = 10) |>
  dplyr::mutate(mpg_plot = mpg / max(mpg)) |>
  dplyr::select(cyl, mpg_plot) |>
  aggrid() |>
  ag_col_render(mpg_plot,
    cellRenderer = "agSparklineCellRenderer",
    cellRendererParams = list(
      sparklineOptions = list(
        type = "bar",
        valueAxisDomain = c(0, 1)
      )
    )
  )
```

## Row group

```{r}
aggrid(iris) |>
  ag_col_def(Species, rowGroup = T)
```

## Accessories

### statusBar

Default has statusBar, you can set it `FALSE` use `ag_gridOptions()`:
```{r}
aggrid(iris) |>
  ag_gridOptions(statusBar = FALSE)
```

### Side Bar

```{r}
aggrid(iris) |>
  ag_gridOptions(sideBar = TRUE)
```

Custom Side bar:

```{r}
aggrid(iris) |>
  ag_gridOptions(sideBar = list(
    toolPanels = list(
      list(
        id = "columns",
        labelDefault = "Columns",
        labelKey = "columns",
        iconKey = "columns",
        toolPanel = "agColumnsToolPanel"
      )
    )
  ))
```

## Charts

```{r}
aggrid(iris) |> 
  enable_charts()
```
