---
title: "Examples"
output:
  html_document:
    toc: true
    toc_float:
      smooth_scroll: false
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Basic Usage

To create aggrid table, use `aggrid()` on a data frame or matrix.

```{r setup}
library(aggrid)
library(dplyr)
library(htmlwidgets)

aggrid(iris)
```

## Column Properties

### Columns: Width

For column width adjustment, you can use `ag_col_def()` or `ag_col_width()`.

```{r}
aggrid(iris) |>
  ag_col_def(columns = c(Sepal.Length, Sepal.Width), width = 80)
```

```{r}
aggrid(iris) |>
  ag_col_width(c(Sepal.Length, Sepal.Width), width = 80)
```

#### Size Columns to Fit

If you don't want a particular column to be included in the auto resize, you can use `size_to_fit()`. For example, you want the first column to remain fixed width, but all other columns to fill the width of the table.
```{r}
iris |>
  dplyr::relocate(Species) |>
  aggrid() |>
  ag_col_width(Species, width = 400) |>
  ag_size_fit()
```

#### Auto-Size Columns

Auto width to fit the contents of the cells in the column.

```{r}
aggrid(iris) |>
  ag_size_columns()
```

More options please see <https://www.ag-grid.com/javascript-data-grid/column-properties>.

### Columns: filter

`aggrid()` default set columns filter, and automatically identify the data type to select filter mode. If you want to change the default behavior, please use `ag_col_filter()`. 
```{r}
aggrid(iris) |>
  ag_col_filter(Sepal.Length, filter = FALSE) |>
  ag_col_filter(Species, filter = "agTextColumnFilter")
```

More options please see <https://www.ag-grid.com/javascript-data-grid/filter-text/>.

### Columns: pinned

```{r}
aggrid(iris) |>
  ag_col_pinned(Species, pinned = "left")
```

### Columns: Header

By default, `aggrid()` will remove colnames dots, use `ag_col_header()` can custom colnames.

```{r}
aggrid(iris) |>
  ag_col_header(Sepal.Length, headerName = c("Sepal.Length")) |>
  ag_col_header(Sepal.Width, headerName = c("Sepal.Width"))
```

The above code is bad, you can use `ag_col_defs()` for vectorization.

```{r}
aggrid(iris) |>
  ag_col_defs(columns = everything(), headerName = names(iris))
```

[`menuTabs`](ag-grid.com/javascript-data-grid/column-properties/#reference-header-menuTabs) parameter default is `c('filterMenuTab','generalMenuTab','columnsMenuTab')`, 
If you only want to filter menuTab, you can:

```{r}
head(iris, n = 10) |>
  aggrid() |>
  ag_col_def(columns = Species, menuTabs = list("filterMenuTab"))
```

### Columns: group

```{r}
head(iris, n = 10) |>
  aggrid() |>
  ag_col_group(columns = starts_with("Sepal"), headerName = "Sepal")
```

Center header:
```{r}
head(iris, n = 10) |>
  aggrid() |>
  ag_col_group(columns = starts_with("Sepal"), headerName = "Sepal", headerClass = "ag-header-center") |>
  ag_col_group(columns = starts_with("Petal"), headerName = "Petal", headerClass = "ag-header-center")
```

Set all content content center:

```{r}
head(iris, n = 10) |>
  aggrid() |>
  ag_col_group(columns = starts_with("Sepal"), headerName = "Sepal", headerClass = "ag-header-center") |>
  ag_col_group(columns = starts_with("Petal"), headerName = "Petal", headerClass = "ag-header-center") |>
  ag_col_def(cellStyle = list(textAlign = "center"), headerClass = "ag-header-center")
```

### Columns: format

`ag_col_format()` use [numeraljs](http://numeraljs.com/) to format number.

```{r}
data.frame(
  price = c(9603.01, 100, 98322),
  percent = c(0.9525556, 0.5, 0.112),
  exponential = c(123456789, 0.0001314, 0.52),
  bytes = c(1024^3, 1024^2, 1024)
) |>
  aggrid() |>
  ag_col_format(price, "$0,0.000") |>
  ag_col_format(percent, "0.0%") |>
  ag_col_format(exponential, "0,0e+0") |>
  ag_col_format(bytes, "0 b")
```

Custom columns format use `valueFormatter`:

```{r}
data.frame(
  Area = c(1000, 200, 40)
) |>
  aggrid() |>
  ag_col_def(valueFormatter = JS('
    (params) => {return params.value + " mi\u00b2";};
  '))
```

### Coulmns: CellRender

`valueFormatter` mainly used for formatting, and `cellRenderer` use for adding html tags and `cellStyle` use for cell style.

```{r}
data.frame(
  go_term = c("GO:0140359", "GO:0036094", "GO:0048029", "GO:0042626", "GO:0097367"),
  p_value = c(3.30e-07, 1.60473e-06, 2.47191e-01, 1.19e-05, 0.05)
) |>
  aggrid() |>
  ag_col_render(go_term, cellRenderer = JS('(params) => {
    return `<a href="https://amigo.geneontology.org/amigo/term/${params.value}">${params.value}</a>`
  };')) |>
  ag_col_render(p_value, cellStyle = JS('function(params) {
    if (params.value <= 0.05) {
      return { color: "green" };
    } else{
      return { color: "red" };
    }
  }'))
```

> TO DO: need to encapsulate some simple functions to modify the cellRender.

## Sparkline

### line plot and column plot

```{r}
mtcars |>
  dplyr::group_by(cyl) |>
  dplyr::summarize(mpg_line = list(mpg)) |>
  aggrid() |>
  ag_col_render(mpg_line, cellRenderer = "agSparklineCellRenderer")
```

Note in the snippet above that specifying an `agSparklineCellRenderer` will display the data using the default `line` sparkline. 


Sparklines are customised by supplying `sparklineOptions` to the `cellRendererParams` on the Sparkline Cell Renderer as shown below. For example：

### bar plot

```{r}
head(mtcars, n = 10) |>
  dplyr::mutate(mpg_plot = mpg / max(mpg)) |>
  dplyr::select(cyl, mpg_plot) |>
  aggrid() |>
  ag_col_render(mpg_plot,
    cellRenderer = "agSparklineCellRenderer",
    cellRendererParams = list(
      sparklineOptions = list(
        type = "bar",
        valueAxisDomain = c(0, 1)
      )
    )
  )
```

## Row group

```{r}
aggrid(iris) |>
  ag_col_def(Species, rowGroup = T)
```

> ps: Currently does not support server mode, welcome to contribute.

## Accessories

### statusBar

Default has statusBar, you can set it `FALSE` use `ag_gridOptions()`:
```{r}
aggrid(iris) |>
  ag_gridOptions(statusBar = FALSE)
```

### Side Bar

```{r}
aggrid(iris) |>
  ag_gridOptions(sideBar = TRUE)
```

Custom Side bar:

```{r}
aggrid(iris) |>
  ag_gridOptions(sideBar = list(
    toolPanels = list(
      list(
        id = "columns",
        labelDefault = "Columns",
        labelKey = "columns",
        iconKey = "columns",
        toolPanel = "agColumnsToolPanel"
      )
    )
  ))
```

## Charts

```{r}
aggrid(iris) |> 
  enable_charts()
```
