---
title: "Examples"
output:
  html_document:
    toc: true
    toc_float:
      smooth_scroll: false
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Basic Usage

To create aggrid table, use `aggrid()` on a data frame or matrix.

```{r setup}
library(aggrid)
aggrid(iris)
```

## Column Properties

### Columns: Width

For column width adjustment, you can use `ag_col_def()` or `ag_col_width()`.

```{r}
aggrid(iris) |> 
  ag_col_def(columns = c(Sepal.Length,Sepal.Width),width = 80)
```

```{r}
aggrid(iris) |> 
  ag_col_width(c(Sepal.Length,Sepal.Width),width = 80)
```

#### Size Columns to Fit

If you don't want a particular column to be included in the auto resize, you can use `size_to_fit()`. For example, you want the first column to remain fixed width, but all other columns to fill the width of the table.
```{r}
iris |> 
  dplyr::relocate(Species) |> 
  aggrid() |> 
  ag_col_width(Species,width = 400) |> 
  ag_size_fit()
```

#### Auto-Size Columns

Auto width to fit the contents of the cells in the column.

```{r}
aggrid(iris) |> 
  ag_size_columns()
```

More options please see <https://www.ag-grid.com/javascript-data-grid/column-properties>.

### Columns: filter

`aggrid()` default set columns filter, and automatically identify the data type to select filter mode. If you want to change the default behavior, please use `ag_col_filter()`. 
```{r}
aggrid(iris) |> 
  ag_col_filter(Sepal.Length,filter = FALSE) |> 
  ag_col_filter(Species,filter = "agTextColumnFilter")
```

More options please see <https://www.ag-grid.com/javascript-data-grid/filter-text/>.

### Columns: pinned

```{r}
aggrid(iris) |> 
  ag_col_pinned(Species,pinned = "left")
```

### Columns: Header

By default, `aggrid()` will remove colnames dots, use `ag_col_header()` can custom colnames.

```{r}
aggrid(iris) |> 
  ag_col_header(Sepal.Length,headerName = c("Sepal.Length")) |> 
  ag_col_header(Sepal.Width,headerName = c("Sepal.Width"))
```

The above code is bad, you can use `ag_col_defs()` for vectorization.

```{r}
aggrid(iris) |> 
  ag_col_defs(columns = everything(),headerName = names(iris))
```

[`menuTabs`](ag-grid.com/javascript-data-grid/column-properties/#reference-header-menuTabs) parameter default is `c('filterMenuTab','generalMenuTab','columnsMenuTab')`, 
If you only want to filter menuTab, you can:

```{r}
aggrid(iris) |> 
  ag_col_def(columns = Species,menuTabs = list('filterMenuTab'))
```

### Columns: group

```{r}
aggrid(iris) |> 
  ag_col_group(columns = starts_with("Sepal"),headerName = "Sepal")
```

Center header:
```{r}
aggrid(iris) |> 
  ag_col_group(columns = starts_with("Sepal"),headerName = "Sepal",headerClass = "ag-header-center") |> 
  ag_col_group(columns = starts_with("Petal"),headerName = "Petal",headerClass = "ag-header-center")
```

Set all content content center:

```{r}
aggrid(iris) |> 
  ag_col_group(columns = starts_with("Sepal"),headerName = "Sepal",headerClass = "ag-header-center") |> 
  ag_col_group(columns = starts_with("Petal"),headerName = "Petal",headerClass = "ag-header-center") |> 
  ag_col_def(cellStyle = list(textAlign = "center"),headerClass = 'ag-header-center')
```

### Columns: format

`ag_col_format()` use [numeraljs](http://numeraljs.com/) to format number.

```{r}
data.frame(
    price = c(9603.01, 100, 98322),
    percent = c(0.9525556, 0.5, 0.112),
    exponential = c(123456789,0.0001314,0.52),
    bytes = c(1024^3,1024^2,1024)
) |> 
  aggrid() |> 
  ag_col_format(price,"$0,0.000") |> 
  ag_col_format(percent,"0.0%") |> 
  ag_col_format(exponential,"0,0e+0") |> 
  ag_col_format(bytes,"0 b")
```

Custom columns format use `valueFormatter`:

```{r}
data.frame(
  Area = c(1000,200,40)
) |> 
  aggrid() |> 
  ag_col_def(valueFormatter = JS('
    (params) => {return params.value + " mi\u00b2";};
  '))
```

## Row group

```{r}
aggrid(iris) |> 
  ag_col_def(Species,rowGroup = T)
```

## Accessories

### statusBar

Default has statusBar, you can set it `FALSE` use `ag_gridOptions()`:
```{r}
aggrid(iris) |> 
  ag_gridOptions(statusBar = FALSE)
```

### Side Bar

```{r}
aggrid(iris) |> 
  ag_gridOptions(sideBar = TRUE)
```

Custom Side bar:

```{r}
aggrid(iris) |> 
  ag_gridOptions(sideBar = list(
    toolPanels = list(
      list(
        id = 'columns',
        labelDefault = 'Columns',
        labelKey = 'columns',
        iconKey = 'columns',
        toolPanel = 'agColumnsToolPanel'
      )
    )
  ))

```
